---
title: "Email_to_friend"
author: "Estelle"
date: "5/24/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## RE: Movies

Hey Friend 

I took the time to look into our discussion on movie ratings with some data.
```{r include=FALSE}
library(tidyverse)
list.files('/Code/Q1/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```


Check my findingsm addressing your points:

* I firmly remember that Rotten Tomatoes was always a great review platform - and if a
movie had a rating of more than 80% on Rotten Tomatoes, audiences would rate it above
85% every time."

Take a look at this simple and clear table showing that your first claim is not true. Only two of the ROtten Tomatoes over 80% rated films is rated over 85% by Audiences.
```{r}
library(huxtable)
Ratings_comparison_table()
```

* Disney films may not have the highest grossing numbers, but they’ve always been the
most profitable of all the leading studios."
This is not necessarily true according to this graph, so sorry you will need to hold back on the confidence of a statement like that as these colourful dots help show Disney is not always top of the lot for profitability
```{r}
plot1.2()
```


* Audiences are always drawn to the highest grossing films. In fact, I bet the correlation
between the world wide grossing numbers and audience scores would be near 80%.

This graph shows the relationship between Grossing numbers and Audience scores is complex as it follows a pattern that switches from a negative to a positive correlation and so an overall correlation of 80% cannot be claimed unfortunately

```{r}
Regression_Plot(Movies)
```

