---
title: "Readme"
author: "Estelle"
date: "5/24/2021"
output: md_document
variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is the Readme for the assignment for Nico to mark
 
# Question 1

I read the data in 
```{r message=FALSE}
Movies<-Read1("C:/Users/Jamie/Documents/R/Datascience/19818157/Data/Practical/Movies/Movies.csv")
```
And make sure my code is sourced
```{r}
list.files('Code/Q1/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```

And do some analytics to show my friend what the data says on her points.
Below shows a table of all the films that Rotten tomatoes scored over 80%, only two have audience scores over 85% proving my friend wrong.
```{r}
Ratings_comparison_table()
```
# Question 2

# Question 3
Since I require a formal Texevier document I load the template into my settings folder to be able to copy
```{r message=FALSE}
create_template("Settings")
```
I can now edit the template to discuss and present my findings as the pdf output will show.

For this document I create the following plot
```{r}

```

